\chapter*{Acknowledgements}
%===================================================================

I wish to extend my deepest gratitude and appreciation to everyone who has contributed significantly to the successful completion of this project.

My sincere thanks go to Irene Lopez and Andrew Xue, my host and co-host at Google Zurich, for their invaluable guidance, support, and trust throughout my internship. Their mentorship and kindness made this experience not only enriching but truly transformative.

Thank you to the YouTube Developer Infrastructure team for their warm welcome, collaborative spirit, and continuous encouragement, and to my mentor Veronica Radu, whose insights and support greatly contributed to my personal and professional growth.

I also wish to thank Mrs. Rabaa Youssef, my academic supervisor, for accompanying me in this final academic milestone.

To the distinguished members of the jury, I am grateful for your time and consideration in reviewing my work. I hope this report lives up to the standards expected of a graduation project.

To the professors of the National Institute of Applied Sciences and Technology, thank you for playing a vital role in shaping my academic and professional foundation.

And to my family and friends, your unwavering belief in me has carried me through the most demanding moments. Thank you for your love, patience, and presence.

Finally, a quiet note of gratitude to myself for the perseverance and dedication that made this journey possible.